---
title: "Assignment_3_Doing_DS"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown


Question 1: 

Deeptis-Air:~ Shantanu$ mkdir gitrepo <br />
Deeptis-Air:~ Shantanu$ cd gitrepo <br />
Deeptis-Air:gitrepo Shantanu$ git clone https://github.com/awesomedata/awesome-public-datasets.git <br />
Cloning into 'awesome-public-datasets'... <br />
remote: Counting objects: 1484, done. <br />
remote: Total 1484 (delta 0), reused 0 (delta 0), pack-reused 1484 <br />
Receiving objects: 100% (1484/1484), 565.76 KiB | 303.00 KiB/s, done. <br />
Resolving deltas: 100% (866/866), done. <br />
Deeptis-Air:gitrepo Shantanu$ <br />

Question 2: A

```{r}

getwd()
file = "/Users/Shantanu/gitrepo/awesome-public-datasets/Datasets/titanic.csv"
Titanic.data = read.csv(file=file,head=TRUE,sep=",")
nrow(Titanic.data)

head(Titanic.data)
```

Question 2: B

```{r}

n.male = 0
n.female = 0

for  (i in 1:nrow(Titanic.data)){
  
record = Titanic.data[i,] 

if (record$Sex == 'male' | record$Sex == 'Male') {
  
  n.male = n.male + 1

  }

else if (record$Sex == 'female' | record$Sex == 'Female') {  
  
  n.female = n.female + 1
    
  }
  
}
  

gender_dist = data.frame(Male=n.male, Female=n.female)

barplot(as.matrix(gender_dist), beside = TRUE, ylim = c(0,700), main = 'Gender Distribition')
```

Question 2. C

```{r}

lapply(Titanic.data['Fare'], mean)

lapply(Titanic.data['Survived'], mean)
# Assuming here that the mean of the column survived was asked in the question

sapply(Titanic.data['Age'],mean,na.rm=TRUE)


```

Question 3.

```{r}

getwd()
file = "/Users/Shantanu/Data_Files/sleep_data_01.csv"
Sleep.data = read.csv(file=file,head=TRUE,sep=",")
nrow(Sleep.data)
head(Sleep.data)


```


3A.



```{r}




# Median Age

func.basic.stats.median <- function(my_vector) {

x = median(my_vector, na.rm = TRUE)

return(x)

}


# Minimum Sleep

func.basic.stats.min <- function(my_vector) {

x = min(my_vector, na.rm = TRUE)
return(x)

}



# Maximum Sleep

func.basic.stats.min <- function(my_vector) {

x = max(my_vector, na.rm = TRUE)
return(x)

}


# Mean

func.basic.stats.mean <- function(my_vector) {

x = mean(my_vector, na.rm = TRUE)
return(x)

} 


# Standard Diev

func.basic.stats.sd <- function(my_vector) {

x = sd(my_vector, na.rm = TRUE)
return(x)

} 


```

Question 3.b

```{r}


change.column.names <- function(passed.df){
  
  colnames(passed.df)[1] <- "MedianAge"
  colnames(passed.df)[2] <- "SelfEsteem"
  colnames(passed.df)[3] <- "SE_SD"
  colnames(passed.df)[4] <- "DurationRange"
  
  return(passed.df)
  
}

func.operations.df <- function(passed.df){
  
sleep.study.median.age = median(passed.df[,'Age'], na.rm = TRUE)

sleep.study.min.sleep = min(passed.df[ ,'Duration'], na.rm = TRUE)
sleep.study.min.sleep

sleep.study.max.sleep = max(passed.df[ ,'Duration'], na.rm = TRUE)
sleep.study.max.sleep

sleep.study.mean.RSES = mean(passed.df[ ,'RSES'], na.rm = TRUE)
sleep.study.mean.RSES
 
sleep.study.sd.RSES = sd(passed.df[ ,'RSES'], na.rm = TRUE)
sleep.study.sd.RSES

report <- data.frame( m_age = sleep.study.median.age,
                  RSES_Mean = sleep.study.mean.RSES,
                  sdupon5 = (sleep.study.sd.RSES/5),
                  rng = (sleep.study.max.sleep - sleep.study.min.sleep))


report = change.column.names(report)

report[] <- lapply(report, function(x) if(is.numeric(x)) round(x, 2) else x)

return(report)
  
}

report = func.operations.df(Sleep.data)

report

```

Q4.


```{r}

library(fivethirtyeight)

data(package = "fivethirtyeight")

college_grads <- college_recent_grads

# https://github.com/rudeboybert/fivethirtyeight/tree/master/docs/articles

head(college_grads)

dim (college_grads)

colnames(college_grads)

```

Q5.

```{r}

colnames(college_grads)
ncol(college_grads)

library(tidyverse)
library(dplyr)

count_cat = college_grads %>% count(major_category)

values = count_cat$n

arguments = count_cat$major_category

par(las=2)
barplot(values,names.arg = arguments, horiz = TRUE, xlim=c(0,40), main = 'Graduate College Category Counts')

write.csv(count_cat,"CountCat.csv",row.names = FALSE)
write.csv(college_grads,"CollegeGradsData.csv",row.names = FALSE)


```

Q6:

GitHub Link: https://github.com/Shangodbole/SMUMSDS_HW.git















